An HPSG account for verbal reduplication in Mandarin Chinese

### 2023-06-08 chapters/ch01-Intro.tex
Update 2023-06-08-15:59:49

In Mandarin Chinese, verbs can be reduplicated to express a delimitative aspectual meaning \citep[e.g.][]{Chao1968, LiThompson1981,  Li1996, Dai1997,  Zhu1998, Xing2000, Chen2001,  Tsao2001, Yang2003, XiaoMcEnery2004}. 
This means that the event or state denoted by the verb happens in a short duration and/or a low frequency \citep[155]{XiaoMcEnery2004}, such as illustrated in (\ref{ex:redup-ex}).\footnote{Reduplications
    in the example sentences will be set in italics.}
Thus, verbal reduplication in Mandarin Chinese is often translated as doing something ``a little bit/for a little while”.

>>>>

In Mandarin Chinese, verbs can be reduplicated to express a delimitative aspectual meaning (e.g. \citealt[204--205]{Chao1968}; \citealt[29]{LiThompson1981};  \citealt[14]{Li1996}; \citealt[67]{Dai1997};  \citealt[382--383]{Zhu1998}; \citealt[420--421]{Xing2000}; \citealt[48]{Chen2001};  \citealt[288]{Tsao2001}; \citealt[11--12]{Yang2003}; \citealt[Sec. 4.3]{XiaoMcEnery2004}). 
This means that the event or state denoted by the verb happens in a short duration and/or a low frequency \citep[155]{XiaoMcEnery2004}, such as illustrated in (\ref{ex:redup-ex}).\footnote{Reduplications
    in the example sentences will be set in italics.}
Thus, verbal reduplication in Mandarin Chinese is often translated as doing something ``a little bit/for a little while”.

### 2023-06-08 chapters/ch02-Phenomenon.tex
Update 2023-06-08-15:59:49

There is no general agreement on the forms of verbal reduplication in Mandarin Chinese.
We adopt a broad definition in terms of the forms of verbal reduplication in Mandarin Chinese 
and list in (\ref{ex:redup-forms}) all the forms commonly discussed in the literature.

@@

\ea\label{ex:redup-forms}
	\ea for monosyllabic verbs: \textit{shuo} `say'
		\ea \gll shuo-shuo\\
		say-say\\\jambox{AA}
		\ex \gll shuo-yi-shuo\\
		say-one-say\\\jambox{A-\textit{yi}-A}
		\ex \gll shuo-le-shuo\\
		say-\textsc{pfv}-say\\\jambox{A-\textit{le}-A}
		\ex \gll shuo-le-yi-shuo\\
		say-\textsc{pfv}-one-say\\\jambox{A-\textit{le}-\textit{yi}-A}
		\ex \gll shuo-shuo-kan\\
		say-say-look\\\jambox{AA-\textit{kan}}
		\ex \gll shuo-kan-kan\\
		 say-look-look\\\jambox{A-\textit{kan}-\textit{kan}}
		\z
	\ex for disyllabic verbs: \textit{lai-wang} come-go `come and go/communicate'
		\ea \gll lai-wang-lai-wang\\
		come-go-come-go\\ \jambox{ABAB}
		\ex \gll lai-wang-le-lai-wang\\
		come-go-\textsc{pfv}-come-go\\ \jambox{AB-\textit{le}-AB}
		\ex \gll lai-lai-wang-wang\\
		come-come-go-go\\ \jambox{AABB}
		\z
	\ex\label{ex:forms-VO} for V-O compounds: \textit{shuo-huang} tell-lie `lie'
		\ea \gll shuo-shuo-huang\\
		tell-tell-lie\\ \jambox{AAB}
		\ex \gll shuo-yi-shuo-huang\\
		tell-one-tell-lie\\ \jambox{A-\textit{yi}-AB}
		\ex \gll shuo-le-shuo-huang\\
		tell-\textsc{pfv}-tell-lie\\ \jambox{A-\textit{le}-AB}
		\z
	\z
\z

@@

The reduplication has a similar syntactic distribution as an unreduplicated verb (\ref{ex:redup-syn}). 
The reduplication cannot be aspect marked, though, except with the perfective aspect marker \textit{le} (for further discussions see Section \ref{sec:aspM}). 
The reduplication is incompatible with an expression that quantifies the duration or the extent of the event expressed in the sentence (\ref{ex:redup-quan}) \citetext{\citealp[114--115]{Chen2005}; \citealp[83--84]{Li1998}}.
This is probably because the reduplication already contains a quantity meaning \citetext{\citealp[114--115]{Chen2005}; \citealp[84]{Li1998}}, namely a short duration or a small extent.

\ea\label{ex:redup-syn}
	\ea Intransitive verb:
		\ea \gll ta xiao-le.\\
		he laugh-\textsc{pfv}\\
		\glt `He laughed.'
		\ex \gll ta \textit{xiao}-\textit{le}-\textit{xiao}.\\
		he laugh-\textsc{pfv}-laugh\\
		\glt `He laughed a little bit.'
		\z
	\ex Transitive verb:
		\ea \gll ni wen ta.\\
		you ask him\\
		\glt `Ask him.'
		\ex \gll ni \textit{wen}-\textit{(yi)}-\textit{wen} ta.\\
		you ask-(one)-ask he\\
		\glt `Try to ask him.'
		\z
	\ex Under negation:
		\ea \gll weishenme wo bu kan ta qita fangmian de jinbu he quanfangwei de chengzhang\\
		why I not look he other aspect \textsc{de} progress and all-round \textsc{de} growth\\
		\glt `Why don't I look at his progress in other aspects and all-round growth?'
		\ex \gll weishenme wo bu \textit{kan}-\textit{kan} ta qita fangmian de jinbu he quanfangwei de chengzhang\\
		why I not look-look he other aspect \textsc{de} progress and all-round \textsc{de} growth\\ \jambox{({CCL})}
		\glt `Why don't I look a little bit at his progress in other aspects and all-round growth?'
		\z
	\ex In \textit{ba}-construction:
		\ea \gll gou-mai zhiqian zhen gai ba qingkuang mo qingchu.\\
		purchase-buy before really should \textsc{ba} situation touch clearly\\
		\glt `(I) should really check the situation clearly before I make the purchase.'
		\ex \gll gou-mai zhiqian zhen gai ba qingkuang \textit{mo}-\textit{mo} qingchu.\\
		purchase-buy before really should \textsc{ba} situation touch-touch clearly\\ \jambox{({CCL})}
		\glt `(I) should really quickly check the situation clearly before I make the purchase.'
		\z
	\ex With modal verb:
		\ea \gll you liang ben shu ni-men keyi kan \ldots\\
		there.be two \textsc{clf} book you-\textsc{pl} can read\\
		\glt `There are two books that you can read \ldots'
		\ex \gll you liang ben shu ni-men keyi \textit{kan}-\textit{kan} \ldots\\
		there.be two \textsc{clf} book you-\textsc{pl} can read-read\\ \jambox{({CCL})}
		\glt `There are two books that you can read a little bit \ldots'
		\z
	\ex In Serial Verb Construction (SVC):
		\ea \gll ta dao jinian-tang dong-ce de yi chu chongxi-bu qing shifu bangmang kan nali chu-le wenti.\\
		she go.to memorial-hall east-side \textsc{de} one place film.developing-department ask master help look where come.out-\textsc{pfv} problem\\
		\glt `She went to a film developing department at the east side of the memorial hall to ask the master to help have a look at where went wrong.'
		\ex \gll ta dao jinian-tang dong-ce de yi chu chongxi-bu qing shifu bangmang \textit{kan}-\textit{kan} nali chu-le wenti.\\
		she go.to memorial-hall east-side \textsc{de} one place film.developing-department ask master help look-look where come.out-\textsc{pfv} problem\\ \jambox{({CCL})}
		\glt `She went to a film developing department at the east side of the memorial hall to ask the master to help have a quick look at where went wrong.'
		\z
	\ex With an expression of quantity: \label{ex:redup-quan}
		\ea[]{\gll ta yi tian pao shi li.\\
		he one day run ten mile\\ \jambox{\citep[83]{Li1998}}
		\glt `He runs ten miles a day.'}
		\ex[*]{\gll ta yi tian \textit{pao}-\textit{pao} shi li.\\
		he one day run-run ten mile\\}
		\z
	\z
\z

@@

The reduplication has a \textit{delimitativeness} meaning \citep[e.g.][]{Chao1968, Chen2001, Dai1997, Li1996, LiThompson1981, Tsao2001, XiaoMcEnery2004, Xing2000, Yang2003, Zhu1998}. 
To be specific, the reduplication of [$+$durative] verbs reduces the duration of the events,
and the reduplication of [$-$durative] verbs reduces the iteration frequency of the events \citetext{\citealp[14]{Li1996}; \citealp[149--150]{XiaoMcEnery2004}}.
Besides delimitativeness, \citet{Chao1968}, \citet{Fan1964}, \citet{Li1996}, \citet{Smith1991, Smith1994} and \citet{Tsao2001} suggested that the reduplication signifies \textit{tentativeness}, which can be used
``to refer modestly to one's own activities, or for mild imperatives'' \citep[356]{Smith1991}, or ``trying to'' do something \citep[234]{LiThompson1981}.
\textit{Frequentativeness} or \textit{habitualness}, that the event denoted by the verb happens frequently or habitually, is mentioned by \citet{Fan1964}, \citet{Li1996} and \citet{Qian2000} as the meaning of reduplication, as well.
 \citet{Fan1964} further proposed a meaning of \textit{slightness} or \textit{casualness} for reduplication, which implies that the event is unimportant or conveys a casual attitude of the speaker.
 \citet{Zhu1998} suggested that the main function of reduplication is to \textit{increase the agency} of the action or the change denoted by the verb.

@@

@@

\ea\label{ex:nonvol}
\ea
\gll keshi xian mujin, dajia ye zhihao \textit{weiqu-weiqu} le.\\
but now current everybody also can.only feel.wronged-feel.wronged \textsc{ptc}\\ \jambox{({CCL})}
\glt `But now, everybody can only feel wronged a little bit.'

\ex
\gll ta-men neng zuo de buguo shi \textit{ren-ren-xing} shua dian'er xiao piqi \textit{diao-diao} yanlei shenme de.\\
she-\textsc{pl} can do \textsc{de} just be be.willful-be.willful-temperament play a.little small temper drop-drop tear what \textsc{de}\\ \jambox{({CCL})}
\glt `What they can do is just to be a little bit willful, to lose their temper a little bit and to drop a little bit of tears or something.'
\z
\z

@@

@@

@@

\citet[Ch. 4]{XiaoMcEnery2004} considered \textit{le}, \textit{guo} and reduplication to indicate perfective aspects, as they all view the situation as an inseparable whole.
The perfective aspect marker \textit{le} is compatible with reduplication while the experiential aspect marker \textit{guo} is not.
\citet[128--131]{XiaoMcEnery2004} described that \textit{le} has the semantic feature of dynamicity, since it ``can focus on both heterogeneous internal structures and changing points'' \citep[129]{XiaoMcEnery2004}.
It can be combined with a situation with a dynamic internal structure, such as crying in (\ref{ex:cry}).
It can also co\hyp{}occur with a situation with a change at a certain time point, such as getting to know in (\ref{ex:know}).

@@

On the other hand, the experiential aspect marker \textit{guo} cannot co\hyp{}occur with a reduplicated verb, 
because its dynamicity attributes to an ``experiential change'' \citep[148]{XiaoMcEnery2004}, 
namely that a situation has been experienced historically and that ``the final state of the situation no longer obtains'' at the reference time \citep[144]{XiaoMcEnery2004}. 
Compare (\ref{ex:guo-dyn}) and (\ref{ex:le-dyn}), \textit{guo} in (\ref{ex:guo-dyn}) suggests a change out of the state of being a soldier, 
whereas \textit{le} in (\ref{ex:le-dyn}) conveys a change into the state of being a soldier \citep[149]{XiaoMcEnery2004}.

@@

@@

The two groups also have different input and output constraints. \citet{Xie2020} claimed that only dynamic and volitional verbs can undergo AA or ABAB reduplication (but see Section~\ref{sec:Aktionsarten}).
On the other hand, AABB requires its input to be a complex verb whose constituents are either synonymous, antonymous or logically coordinated (\ref{ex:AABB-input}). 
Moreover, as can be seen in the translation in (\ref{ex:AABB-input}), the output of AABB has an increasing meaning, i.e. an event happens repeatedly or continuously, as opposed to the delimitative meaning of AA and ABAB.

@@

The first syntactic test is phrasal extension, namely the addition of optional elements \citetext{\citealp[150]{Duanmu1998}; \citealp[280]{Schaefer2009}}. 
Optional elements that can possibly appear in a phrase should be able to be added into it,
and subparts of a phrase should be able to be modified separately. 
If the unit is a word, however, then neither of these should  be possible.
As illustrated in (\ref{ex:redup-forms}) in Section~\ref{sec:forms}, the reduplication can only be separated by \textit{le} and \textit{yi}. 
As mentioned above, whether aspect markers are considered to be morphological or syntactic elements depends on the theoretical framework (and possibly the target language).\footnote{For example, \citet{Huangetal2009} and \citet{MuellerLipenkova2013} considered aspect markers in Mandarin Chinese to be morphological elements. E.g. \citet{Travis2000, Arcodiaetal2014, BascianoMelloni2017} considered aspect information to be syntactically encoded.} 
And the status of \textit{yi} is unclear, since it does not carry any additional meaning or grammatical function in the structure. % (more on this topic see Section \ref{sec:jackendoff}).
Turning to separate modification,  element in the reduplication cannot be modified individually. 
Compared to (\ref{ex:ext-redup1}), where the adverbial \textit{qingsheng de} `quietly' modifies the whole reduplication, (\ref{ex:ext-redup2}) is ungrammatical, 
as the adverbial cannot modify the second element in the reduplication alone.
It is worth mentioning that in (\ref{ex:ext-redup1}), it is not possible to analyze \textit{qingsheng de} `quietly' to modify only the first element in the reduplication, 
because the adverbial does not necessarily occur adjacent to the verb, as in (\ref{ex:ext-redup3}), 
and it still modifies the whole predicate.
(\ref{ex:ext-redup1}) and  (\ref{ex:ext-redup3}) have the same meaning.

@@

On the other hand, nothing can intervene in between a Parallel Verb Compound and its subparts cannot be modified separately either (\ref{ex:ext-pvc}).

@@

  \ex\label{ex:ext-svc2}
  \gll ta xinku de zhong cai qinfen de mai.\\
  he hard-workingly \textsc{de} plant vegetables diligently \textsc{de} sell\\
  \glt `He plants vegetables hard-workingly and sells them diligently.'
  \z
\z
All in all, by the test of phrasal extension, reduplications behave more like words than like phrases.

@@

@@

Following the analyses above, it is clear that the reduplication failed all of the tests for phrasal status. 
In comparison, Parallel Verb Compounds failed all the tests as well, whereas {SVC}s passed all of them.
This makes the behavior of the reduplication seems more similar to that of a Parallel Verb Compound than that of an {SVC}.
Therefore, it seems more likely to assume the reduplication to be a morphological process rather than a syntactic one.

>>>>

There is no general agreement on the forms of verbal reduplication in Mandarin Chinese.
We adopt a broad definition in terms of the forms of verbal reduplication in Mandarin Chinese 
and list in (\ref{ex:forms-mono})--(\ref{ex:forms-vo}) all the forms commonly discussed in the literature.

@@

\ea\label{ex:forms-mono} for monosyllabic verbs: \textit{shuo} `say'
	\ea \gll shuo-shuo\\ 
		say-say\\ \jambox{AA}
		\ex \gll shuo-yi-shuo\\
		say-one-say\\ \jambox{A-\textit{yi}-A}
		\ex \gll shuo-le-shuo\\
		say-\textsc{pfv}-say\\ \jambox{A-\textit{le}-A}
		\ex \gll shuo-le-yi-shuo\\
		say-\textsc{pfv}-one-say\\ \jambox{A-\textit{le}-\textit{yi}-A}
		\ex \gll shuo-shuo-kan\\
		say-say-look\\ \jambox{AA-\textit{kan}}
		\ex \gll shuo-kan-kan\\
		 say-look-look\\ \jambox{A-\textit{kan}-\textit{kan}}
		\z

\ex\label{ex:forms-di} for disyllabic verbs: \textit{lai-wang} come-go `come and go/communicate'
		\ea \gll lai-wang-lai-wang\\
		come-go-come-go\\ \jambox{ABAB}
		\ex \gll lai-wang-le-lai-wang\\
		come-go-\textsc{pfv}-come-go\\ \jambox{AB-\textit{le}-AB}
		\ex \gll lai-lai-wang-wang\\
		come-come-go-go\\ \jambox{AABB}
		\z

\ex\label{ex:forms-vo} for V-O compounds: \textit{shuo-huang} tell-lie `lie'
		\ea \gll shuo-shuo-huang\\
		tell-tell-lie\\ \jambox{AAB}
		\ex \gll shuo-yi-shuo-huang\\
		tell-one-tell-lie\\ \jambox{A-\textit{yi}-AB}
		\ex \gll shuo-le-shuo-huang\\
		tell-\textsc{pfv}-tell-lie\\ \jambox{A-\textit{le}-AB}
		\z
\z

@@

The reduplication has a similar syntactic distribution as an unreduplicated verb (\ref{ex:syn-vi})--(\ref{ex:syn-svc}). 
The reduplication cannot be aspect marked, though, except with the perfective aspect marker \textit{le} (for further discussions see \sectref{sec:aspM}). 
The reduplication is incompatible with an expression that quantifies the duration or the extent of the event expressed in the sentence (\ref{ex:syn-quan}) \citetext{ \citealp[83--84]{Li1998}; \citealp[114--115]{Chen2005}}.
This is probably because the reduplication already contains a quantity meaning \citetext{\citealp[84]{Li1998}; \citealp[114--115]{Chen2005}}, namely a short duration or a small extent.

\settowidth\jamwidth{\citep[83]{Li1998}}
\begin{sloppypar}
\ea\label{ex:syn-vi} Intransitive verb:
		\ea \gll ta xiao-le.\\
		he laugh-\textsc{pfv}\\
		\glt `He laughed.'
		\ex \gll ta \textit{xiao}-\textit{le}-\textit{xiao}.\\
		he laugh-\textsc{pfv}-laugh\\
		\glt `He laughed a little bit.'
		\z

\ex Transitive verb:
		\ea \gll ni wen ta.\\
		you ask him\\
		\glt `Ask him.'
		\ex \gll ni \textit{wen}-\textit{(yi)}-\textit{wen} ta.\\
		you ask-(one)-ask he\\
		\glt `Try to ask him.'
		\z

\ex Under negation:
		\ea \gll weishenme wo bu kan ta qita fangmian de jinbu he quanfangwei de chengzhang\\
		why I not look he other aspect \textsc{de} progress and comprehensive \textsc{de} development\\
		\glt `Why don't I look at his progress in other aspects and comprehensive development?'
		\ex \gll weishenme wo bu \textit{kan}-\textit{kan} ta qita fangmian de jinbu he quanfangwei de chengzhang\\
		why I not look-look he other aspect \textsc{de} progress and comprehensive \textsc{de} development\\ \jambox{({CCL})}
		\glt `Why don't I look a little bit at his progress in other aspects and comprehensive development?'
		\z

\ex In \textit{ba}-construction:
		\ea \gll gou-mai zhiqian zhen gai ba qingkuang mo qingchu.\\
		purchase-buy before really should \textsc{ba} situation touch clearly\\
		\glt `(I) should really check the situation clearly before I make the purchase.'
		\ex \gll gou-mai zhiqian zhen gai ba qingkuang \textit{mo}-\textit{mo} qingchu.\\
		purchase-buy before really should \textsc{ba} situation touch-touch clearly\\ \jambox{({CCL})}
		\glt `(I) should really quickly check the situation clearly before I make the purchase.'
		\z

\ex With modal verb:
		\ea \gll you liang ben shu ni-men keyi kan \ldots\\
		there.be two \textsc{clf} book you-\textsc{pl} can read\\
		\glt `There are two books that you can read \ldots'
		\ex \gll you liang ben shu ni-men keyi \textit{kan}-\textit{kan} \ldots\\
		there.be two \textsc{clf} book you-\textsc{pl} can read-read\\ \jambox{({CCL})}
		\glt `There are two books that you can read a little bit \ldots'
		\z

\ex\label{ex:syn-svc} In Serial Verb Construction (SVC):
		\ea \gll ta dao jinian-tang dong-ce de yi chu chongxi-bu qing shifu bangmang kan nali chu-le wenti.\\
		she go.to memorial-hall east-side \textsc{de} one place film.developing-department ask master help look where come.out-\textsc{pfv} problem\\
		\glt `She went to a film developing department at the east side of the memorial hall to ask the master to help have a look at where went wrong.'
		\ex \gll ta dao jinian-tang dong-ce de yi chu chongxi-bu qing shifu bangmang \textit{kan}-\textit{kan} nali chu-le wenti.\\
		she go.to memorial-hall east-side \textsc{de} one place film.developing-department ask master help look-look where come.out-\textsc{pfv} problem\\ \jambox{({CCL})}
		\glt `She went to a film developing department at the east side of the memorial hall to ask the master to help have a quick look at where went wrong.'
		\z

\ex With an expression of quantity: \label{ex:syn-quan}
		\ea[]{\gll ta yi tian pao shi li.\\
		he one day run ten mile\\ \jambox{\citep[83]{Li1998}}
		\glt `He runs ten miles a day.'}
		\ex[*]{\gll ta yi tian \textit{pao}-\textit{pao} shi li.\\
		he one day run-run ten mile\\}
		\z
\z
\end{sloppypar}

@@

The reduplication has a \textit{delimitativeness} meaning (e.g. \citealt[204--205]{Chao1968}; \citealt[29]{LiThompson1981};  \citealt[14]{Li1996}; \citealt[67]{Dai1997};  \citealt[382--383]{Zhu1998}; \citealt[420--421]{Xing2000}; \citealt[48]{Chen2001};  \citealt[288]{Tsao2001}; \citealt[11--12]{Yang2003}; \citealt[Sec. 4.3]{XiaoMcEnery2004}). 
To be specific, the reduplication of [$+$durative] verbs reduces the duration of the events,
and the reduplication of [$-$durative] verbs reduces the iteration frequency of the events \citetext{\citealp[14]{Li1996}; \citealp[149--150]{XiaoMcEnery2004}}.
Besides delimitativeness, \citet{Chao1968}, \citet{Fan1964}, \citet{Li1996}, \citet{Smith1991, Smith1994} and \citet{Tsao2001} suggested that the reduplication signifies \textit{tentativeness}, which can be used
``to refer modestly to one's own activities, or for mild imperatives'' \citep[356]{Smith1991}, or ``trying to'' do something \citep[234]{LiThompson1981}.
\textit{Frequentativeness} or \textit{habitualness}, that the event denoted by the verb happens frequently or habitually, is mentioned by \citet{Fan1964}, \citet{Li1996} and \citet{Qian2000} as the meaning of reduplication, as well.
 \citet{Fan1964} further proposed a meaning of \textit{slightness} or \textit{casualness} for reduplication, which implies that the event is unimportant or conveys a casual attitude of the speaker.
 \citet{Zhu1998} suggested that the main function of reduplication is to \textit{increase the agency} of the action or the change denoted by the verb.

@@

\settowidth\jamwidth{\citep[158]{XiaoMcEnery2004}}

@@

\begin{sloppypar}
\ea\label{ex:nonvol}
\ea
\gll keshi xian mujin, dajia ye zhihao \textit{weiqu-weiqu} le.\\
but now current everybody also can.only feel.wronged-feel.wronged \textsc{ptc}\\ \jambox{({CCL})}
\glt `But now, everybody can only feel wronged a little bit.'

\ex
\gll ta-men neng zuo de buguo shi \textit{ren-ren-xing} shua dian'er xiao piqi \textit{diao-diao} yanlei shenme de.\\
she-\textsc{pl} can do \textsc{de} just be be.willful-be.willful-temperament play a.little small temper drop-drop tear what \textsc{de}\\ \jambox{({CCL})}
\glt `What they can do is just to be a little bit willful, to lose their temper a little bit and to drop a little bit of tears or something.'
\z
\z
\end{sloppypar}

@@

\settowidth\jamwidth{\citep[155]{XiaoMcEnery2004}}

@@

\settowidth\jamwidth{\citep[112]{Chen2005}}

@@

\citet[Ch. 4]{XiaoMcEnery2004} considered \textit{le}, \textit{guo} and reduplication to indicate perfective aspects, as they all view the situation as an inseparable whole.
The perfective aspect marker \textit{le} is compatible with reduplication while the experiential aspect marker \textit{guo} is not.
\citet[128--131]{XiaoMcEnery2004} stated that \textit{le} has the semantic feature of dynamicity, since it ``can focus on both heterogeneous internal structures and changing points'' \citep[129]{XiaoMcEnery2004}.
It can be combined with a situation with a dynamic internal structure, such as crying in (\ref{ex:cry}).
It can also co\hyp{}occur with a situation with a change at a certain time point, such as getting to know in (\ref{ex:know}).

\settowidth\jamwidth{\citep[129]{XiaoMcEnery2004}}

@@

In comparison, the experiential aspect marker \textit{guo} cannot co\hyp{}occur with a reduplicated verb, 
because its dynamicity attributes to an ``experiential change'' \citep[148]{XiaoMcEnery2004}, 
namely that a situation has been experienced historically and that ``the final state of the situation no longer obtains'' at the reference time \citep[144]{XiaoMcEnery2004}. 
Compare (\ref{ex:guo-dyn}) and (\ref{ex:le-dyn}), \textit{guo} in (\ref{ex:guo-dyn}) suggests a change out of the state of being a soldier, 
whereas \textit{le} in (\ref{ex:le-dyn}) conveys a change into the state of being a soldier \citep[149]{XiaoMcEnery2004}.

@@

\settowidth\jamwidth{\citep[85]{Xie2020}}

@@

The two groups also have different input and output constraints. \citet{Xie2020} claimed that only dynamic and volitional verbs can undergo AA or ABAB reduplication (but see \sectref{sec:Aktionsarten}).
in comparison, AABB requires its input to be a complex verb whose constituents are either synonymous, antonymous or logically coordinated (\ref{ex:AABB-input}). 
Moreover, as can be seen in the translation in (\ref{ex:AABB-input}), the output of AABB has an increasing meaning, i.e. an event happens repeatedly or continuously, as opposed to the delimitative meaning of AA and ABAB.

@@

The first syntactic test is phrasal extension, namely the addition of optional elements \citetext{\citealp[150]{Duanmu1998}; \citealp[280]{Schaefer2009}}. 
Optional elements that can possibly appear in a phrase should be able to be added into it,
and subparts of a phrase should be able to be modified separately. 
If the unit is a word, however, then neither of these should  be possible.
As illustrated in (\ref{ex:forms-mono})--(\ref{ex:forms-vo}) in \sectref{sec:forms}, the reduplication can only be separated by \textit{le} and \textit{yi}. 
As mentioned above, whether aspect markers are considered to be morphological or syntactic elements depends on the theoretical framework (and possibly the target language).\footnote{For example, \citet{Huangetal2009} and \citet{MuellerLipenkova2013} considered aspect markers in Mandarin Chinese to be morphological elements. E.g. \citet{Travis2000, Arcodiaetal2014, BascianoMelloni2017} considered aspect information to be syntactically encoded.} 
And the status of \textit{yi} is unclear, since it does not carry any additional meaning or grammatical function in the structure. % (more on this topic see Section \ref{sec:jackendoff}).
Turning to separate modification,  the element in the reduplication cannot be modified individually. 
Compared to (\ref{ex:ext-redup1}), where the adverbial \textit{qingsheng de} `quietly' modifies the whole reduplication, (\ref{ex:ext-redup2}) is ungrammatical, 
as the adverbial cannot modify the second element in the reduplication alone.
It is worth mentioning that in (\ref{ex:ext-redup1}), it is not possible to analyze \textit{qingsheng de} `quietly' to modify only the first element in the reduplication, 
because the adverbial does not necessarily occur adjacent to the verb, as in (\ref{ex:ext-redup3}), 
and it still modifies the whole predicate.
(\ref{ex:ext-redup1}) and  (\ref{ex:ext-redup3}) have the same meaning.

@@

Nothing can intervene between a Parallel Verb Compound and its subparts cannot be modified separately either (\ref{ex:ext-pvc}).

@@

  \ex\label{ex:ext-svc2}
  \gll ta xinku de zhong cai qinfen de mai.\\
  he hardworkingly \textsc{de} plant vegetables diligently \textsc{de} sell\\
  \glt `He plants vegetables hard-workingly and sells them diligently.'
  \z
\z
All in all, by the test of phrasal extension, reduplications behave more like words than like phrases.

@@

\settowidth\jamwidth{\citep[137]{Duanmu1998}}

@@

Following the analyses above, it is clear that the reduplication failed all of the tests for phrasal status. 
In comparison, Parallel Verb Compounds failed all the tests as well, whereas {SVC}s passed all of them.
This makes the behavior of the reduplication seem more similar to that of a Parallel Verb Compound than that of an {SVC}.
Therefore, it seems more appropriate to assume reduplication to be a morphological process rather than a syntactic one.

### 2023-06-08 chapters/ch05-Analysis.tex
Update 2023-06-08-15:59:49

\footnotetext[17]{\textit{Yuanqu xuan: Luzhailang [Selected Yuanqu: Luzhailang]}, as cited in \citet[15]{Zhang2000}}
\footnotetext[18]{\textit{Yuan Ming juan: Piaotongshi [Yuan and Ming volume: Piaotongshi]}, 308, as cited in \citet[15]{Zhang2000}}
\footnotetext[19]{Rou, Shi. 1975. \textit{Roushi xiaoshuo xuanji [Selected novels of Roushi]}, 31. Beijing: People's Literature Publishing House.}
\footnotetext[20]{Li, Jieren. 1962. \textit{Da bo [Great wave]}, vol. 3, 171. Beijing: The Writers Publishing House.}
\ea\label{ex:ABleyiAB}
\ea\label{ex:AByiAB-lu}
\gll ni yu wo \textit{zhengli-yi-zhengli}.\footnotemark\\
you let me arrange-one-arrange\\
\glt `Let me arrange it a little bit!'

@@

\ex\label{ex:ABleyiAB-ccl}
\gll jiduo sanluan-zhe de chuan li de dengguang, ye huyinhumie de \textit{bianhuan-le-yi-bianhuan} weizhi.\\
many scattered-\textsc{dur} \textsc{de} boat in \textsc{de} light also flicker \textsc{de} change-\textsc{pfv}-one-chang position\\ \hfill {(CCL)}
\glt `Many scattered lights in the boats also changed their positions a little bit, flickering.'
\z
\z

@@

\ea\label{ex:AyiAkan}
\ea
\gll teyi gongneng de yanjiuzhe-men bufang ruci \textit{shi-yi-shi-kan} \ldots\\
special power \textsc{de} researcher-\textsc{pl} may.as.well such try-one-try-look\\ \hfill {(CCL)}
\glt `Researchers of special power may as well have a try as such as see \ldots'

\ex 
\gll danshi dui fa mei fa-guo hege-zheng, yijing shuo bu qing le, xuyao \textit{cha-yi-cha-kan}.\\
but about issue not issue-\textsc{exp} conformity-certificate already say not clealy \textsc{ptc} need check-one-chek-look\\ \hfill {(CCL)}
\glt `But one already cannot say it clearly anymore, whether a certificate of conformity is issued or not. One needs to have a check and see.'

\ex
\gll rang wo lai \textit{cai-yi-cai-kan}.\\
let I come guess-one-guess-look\\ \hfill {({CCL})}
\glt `Let me have a guess.'

\ex
\gll da-laoban-men yao \textit{deng-yi-deng-kan}\\
big-boss-\textsc{pl} need wait-one-wait-look\\ \hfill {(CCL)}
\glt `Big bosses need to wait a little bit and see.'

\ex
\gll furen ni dao \textit{shu-yi-shu-kan}, zhe zhu hua de huaduo gong you ji zhong yanse.\\
madam you just count-one-count-look this \textsc{clf} flower \textsc{de} blossom in.total have how.many \textsc{clf} color\\ \hfill {(CCL)}
\glt `Madam, just try to count and see how many colors the blossom of this flower has in total.'
\z
\z
Due to the prominent tentative, trying meaning of AA-\textit{kan} and A-\textit{kan}-\textit{kan}, they are not compatible with the perfective aspect marker \textit{le} semantically,
as one usually cannot try something that is already realized.
Thus, structures such as  A\hyp{}\textit{le}\hyp{}A\hyp{}\textit{kan} and A\hyp{}\textit{kan\hyp{}le\hyp{}kan} are considered pragmatically infelicitous.

>>>>

\settowidth\jamwidth{(CCL)}

\footnotetext[17]{\textit{Yuanqu xuan: Luzhailang [Selected Yuanqu: Luzhailang]}, as cited in \citet[15]{Zhang2000}}
\footnotetext[18]{\textit{Yuan Ming juan: Piaotongshi [Yuan and Ming volume: Piaotongshi]}, 308, as cited in \citet[15]{Zhang2000}}
\footnotetext[19]{Rou, Shi. 1975. \textit{Roushi xiaoshuo xuanji [Selected novels of Roushi]}, 31. Beijing: People's Literature Publishing House.}
\footnotetext[20]{Li, Jieren. 1962. \textit{Da bo [Great wave]}, vol. 3, 171. Beijing: The Writers Publishing House.}
\begin{sloppypar}
\ea\label{ex:ABleyiAB}
\ea\label{ex:AByiAB-lu}
\gll ni yu wo \textit{zhengli-yi-zhengli}.\footnotemark\\
you let me arrange-one-arrange\\
\glt `Let me arrange it a little bit!'

@@

\ex\label{ex:ABleyiAB-ccl}
\gll jiduo sanluan-zhe de chuan li de dengguang, ye huyinhumie de \textit{bianhuan-le-yi-bianhuan} weizhi.\\
many scattered-\textsc{dur} \textsc{de} boat in \textsc{de} light also flicker \textsc{de} change-\textsc{pfv}-one-chang position\\ \jambox{(CCL)}
\glt `Many scattered lights in the boats also changed their positions a little bit, flickering.'
\z
\z
\end{sloppypar}

@@

\begin{sloppypar}
\ea\label{ex:AyiAkan}
\ea
\gll teyi gongneng de yanjiuzhe-men bufang ruci \textit{shi-yi-shi-kan} \ldots\\
special power \textsc{de} researcher-\textsc{pl} may.as.well such try-one-try-look\\ \jambox{(CCL)}
\glt `Researchers of special power may as well have a try as such as see \ldots'

\ex 
\gll danshi dui fa mei fa-guo hege-zheng, yijing shuo bu qing le, xuyao \textit{cha-yi-cha-kan}.\\
but about issue not issue-\textsc{exp} conformity-certificate already say not clealy \textsc{ptc} need check-one-chek-look\\ \jambox{(CCL)}
\glt `But one already cannot say it clearly anymore, whether a certificate of conformity is issued or not. One needs to have a check and see.'

\ex
\gll rang wo lai \textit{cai-yi-cai-kan}.\\
let I come guess-one-guess-look\\ \jambox{({CCL})}
\glt `Let me have a guess.'

\ex
\gll da-laoban-men yao \textit{deng-yi-deng-kan}\\
big-boss-\textsc{pl} need wait-one-wait-look\\ \jambox{(CCL)}
\glt `Big bosses need to wait a little bit and see.'

\ex
\gll furen ni dao \textit{shu-yi-shu-kan}, zhe zhu hua de huaduo gong you ji zhong yanse.\\
madam you just count-one-count-look this \textsc{clf} flower \textsc{de} blossom in.total have how.many \textsc{clf} color\\ \jambox{(CCL)}
\glt `Madam, just try to count and see how many colors the blossom of this flower has in total.'
\z
\z
Due to the prominent tentative, trying meaning of AA-\textit{kan} and A-\textit{kan}-\textit{kan}, they are not compatible with the perfective aspect marker \textit{le} semantically,
as one usually cannot try something that is already realized.
Thus, structures such as  A\hyp{}\textit{le}\hyp{}A\hyp{}\textit{kan} and A\hyp{}\textit{kan\hyp{}le\hyp{}kan} are considered pragmatically infelicitous.
\end{sloppypar}
